---
title: "Homework #1 -- Pet Names Dataset"
author: Wejdan Awad
date: "`r Sys.Date()`"
output: github_document
---

**Student ID:2201002744

**Deadline:** 23:59 on Saturday, 13 February 2021

**Total Points:** 30


## Loading Packages

```{r load-packages, message = FALSE}

library(tidyverse)
library(openintro)
library(ggrepel)
```


##Exercises

`1

(4 points)
```{r}

```
Write your narrative here

52519 .


`2.

(4 points)

```{r}

```
Write your narrative below

7 .

`3. Copy the code provided in the homework documentation and paste it here. 

(4 points)

```{r}
seattlepets %>%
count(animal_name, sort = TRUE)
```
Write your narrative here
NA          483
Lucy        439
Charlie     387
Luna        355  

`4.

(10 points)

```{r species-name-top5, eval=TRUE}
 seattlepets %>%
     group_by(species) %>%
     count(animal_name, sort = TRUE) %>%
     slice_max(n, n = 5)%>%arrange(species, n) 
```


`5.  What names are more common for cats than dogs? The ones above the line or the ones below the line?

Answer here

Oliver and lily .

(4 points)

`6. Is the relationship between the two variables (proportion of cats with a given name and proportion of dogs with a given name) positive or negative? What does this mean in context of the data?

Answer here

Positive , if dogs names increase the cats names increase also and also if dogs 
names decrease the cats name decrease also in the same name of THEM .

(4 points)